lab_notebook

### 2018-11-29 lab_notebook.Rmd
edited f_b_rights

###########
11/26/2018

@@

Part 4:
For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).

@@

as_factor <- gdp_rightsbased$i_right
as_factor <- gdp_rightsbased$turf

itq_glm <- glm(i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
turf_glm

@@

>>>>

###########

Part 4:
For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
```{r}

@@

@@

#gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)

itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
#turf_glm

@@

Part 5:
RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.

ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")

f_b_itq <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA")

#write.csv(f_b_itq, file = "f_b_itq.csv")
f_b_irights <- read_csv("data/f_b_irights.csv")

F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 22)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

#F_B_graph
ggplotly(F_B_graph)
